Controlled Experiments for Word Embeddings

### 2015-11-26 article/main.tex
fixes #8 (turn off subsampling)

Notice the inflection of the syn1neg curve in
Figure~\ref{fig:word-frequency-experiment-graph} for \word{the} at
approximately $10^6$.  We have no explanation of this.  Also observe
that the lengths of the vectors representing the meaningless pseudowords
\word{VOID\_i} are approximately constant (about $2.5$).  Since we
already found the direction to be also constant, it is sensible to speak
of the word vector of \word{VOID} irrespective of its frequency.  In
particular, the vector of the pseudoword \word{VOID\_1} may be taken as an approximation.

>>>>

Observe that the lengths of the vectors representing the meaningless pseudowords
\word{VOID\_i} are approximately constant (about $2.5$).  Since we
already found the direction to be also constant, it is sensible to speak
of the word vector of \word{VOID} irrespective of its frequency.  In
particular, the vector of the pseudoword \word{VOID\_1} may be taken as an approximation.
